### 2020-02-08 nlp_models.tex
updated main sections

\michael{WHERE: Highlight difference between $\alpha$ and $\hat{\alpha}$.}
To avoid confusion, let us clarify the differences between $\alpha$ and $\hat{\alpha}$.  
We fit the ESD of the correlation matrix $\mathbf{X}$ to a truncated power law (PL), parameterized by 2 values:
the PL exponent $\alpha$, and the maximum eigenvalue $\lambda_{max}$.  (Technically, we also need the minimum
eigenvalue $\lambda_{min}$, but this detail does not affect our analysis.)
The PL exponent $\alpha$ measures of the 
amount of correlation in a DNN layer weight matrix $\mathbf{W}$.  It is valid for $\lambda<\lambda_{max}$, and
it scale invariant (does not depend on the normalization of $\mathbf{W}$ or $\mathbf{X}$.)
The Weighted-Alpha metric, $\hat{\alpha}=\alpha\log\lambda_{max}$, approximates the log $\alpha$ (Shatten) Norm 
$(\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha})$ (derived using statistical mechanics and RMT \nred{(in progress)}, 
and lets us compute a balanced, weighted average log PL norm metrix for the entire DNN.  
The $\hat{\alpha}$ metric also behaves like an imrpoved, weighted log average Spectral Norm, and may track this metric in some cases.

>>>>

\michael{WHERE: Highlight difference between $\alpha$ and $\hat{\alpha}$.}
To avoid confusion, let us clarify the differences between $\alpha$ and $\hat{\alpha}$.  
We fit the ESD of the correlation matrix $\mathbf{X}$ to a truncated power law (PL), parameterized by 2 values:
the PL exponent $\alpha$, and the maximum eigenvalue $\lambda_{max}$.  (Technically, we also need the minimum
eigenvalue $\lambda_{min}$, but this detail does not affect our analysis.)
The PL exponent $\alpha$ measures of the 
amount of correlation in a DNN layer weight matrix $\mathbf{W}$.  It is valid for $\lambda<\lambda_{max}$, and
it scale invariant (does not depend on the normalization of $\mathbf{W}$ or $\mathbf{X}$.)
The Weighted-Alpha metric, $\hat{\alpha}=\alpha\log\lambda_{max}$, approximates the log $\alpha$ Norm.
$(\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha})$ (derived using statistical mechanics and RMT \nred{(in progress)}, 
and lets us compute a balanced, weighted average log PL norm metrix for the entire DNN.  
The $\hat{\alpha}$ metric also behaves like an imrpoved, weighted log average Spectral Norm, and may track this metric in some cases.
